\section{Considerations for Bandpass Sampling Architectures}
An analog bandpass signal x(t) can be fully reconstructed if it's sampled with a frequency of more than two times the bandwidth of x(t)

Sampled signal
$$
\text { Sampled signal } \quad x_a(t)=x(t) \cdot \sum_{n=-\infty}^{\infty} \delta(t-n T)
$$
$$
\text { Spectrum of the sampled signal } \quad X_a(f)=X(f) *\left[\frac{1}{T} \sum_{n=-\infty}^{\infty} \delta\left(f-\frac{n}{T}\right)\right]
$$

$$
\begin{array}{rlrl} 
& -f_u+k \cdot f_A<f_u & & \frac{2 \cdot f_u}{k}>f_A>\frac{2 \cdot f_O}{k+1} \\
-f_o+(k+1) \cdot f_A>f_o & & \\
& (k+1) \cdot f_u & >k \cdot f_o & 0 \leq k<\frac{f_u}{B} \\
k \cdot f_u+f_u & >k \cdot f_o & & \\
k \cdot\left(f_o-f_u\right) & =k \cdot B<f_u & &
\end{array}
$$
The idea is to get a digital downconversion instead of a analog one, due to sampling theorem.
The problem is that one has mirror from the left side, therefore it would be nice if one can remove it.
Analytic signal has only positive frequency components, is not anymore a real time signal, since a real signal has always a positive and negative part.
\section{Wave propagation}
The frequency response of the channel is given by H(t).
\begin{equation}
\underline{H}(f, t)=\frac{\underline{Y}(f, t)}{\underline{X}(f, t)}
\end{equation}
Important wave progpagations modes
\begin{itemize}
    \item Ground wave propagation\newline
    Wave is conducted by the earths surface (air and earth). The issue with this path is that one has losses (currents in the earth that have a resistance). The higher the frequency the larger the losses get.
    \item Sky wave propagation, we have positively and negatively charger particles in the ionosphere which act as a conductor.
    \item Line of sight (LOS)
\end{itemize}
\subsection{Exercise 13}
\begin{itemize}
    \item \textbf{Image Reject Mixers: Calculate the image rejection ratio at a given phase error of 3$^\circ$ and an amplitude error of 2 dB}\newline
    According to \autoref{eq:image_rejection_ratio} the following holds:
    $$
    I R R^h=\sqrt{\sin ^2\left(\frac{\delta \varphi}{2}\right)+\left(\frac{\delta G}{2 G}\right)^2 \cdot \cos ^2\left(\frac{\delta \varphi}{2}\right)}
    $$
    where $\delta G$ = amplitude error and $\delta \varphi$ = phase error, therefore $\frac{\delta G}{G}=10^{\frac{2}{20}}-1$ = 0.259.
     $$
    I R R^h=\sqrt{\sin ^2\left(\frac{3^{\circ}}{2}\right)+\left(\frac{10^{\frac{2}{20}}-1}{2}\right)^2 \cdot \cos ^2\left(\frac{3^{\circ}}{2}\right)}=17.586dB
    $$
\end{itemize}



%https://github.com/l3v5y/UW-Electronics-Lecture-Notes/blob/master/ES335%20-%20Communication%20Systems.tex
% \begin{figure}[h]
%     \begin{tikzpicture}
%         \draw[->] (1,0) node [below]{$(f_0-f_m)$} -- (1,1) node [above left] {$(\frac{A_0m}{2})$};
%         \draw[->] (7,0) node [below]{$(f_0+f_m)$} -- (7,1) node [above right] {$(\frac{A_0m}{2})$};
%         \draw[->] (4,0) node [below]{$f_0$} -- (4,2) node [above right] {$A_0$};
%         \draw[->] (0,0) -> (8,0) node [below right] {$f(\omega )$};
%         \draw[<->] (1,0.5)--(4,0.5);
%         \node[align=center, above] at (2.5,0.5) {$f_m(\omega_m)$};
%         \node[align=center, above] at (5.5,0.5) {$f_m(\omega_m)$};
%         \draw[<->] (7,0.5)--(4,0.5);
%     \end{tikzpicture}
%     \centering
%     \caption{Spectrum of an AM signal, including sidebands}
% \end{figure}